---
title: "hw4 nihit parikh"
output:
  word_document: default
  html_notebook: default
  pdf_document: default
  html_document:
    df_print: paged
---

```{r}
library(tidyverse)
```
## Get data and preliminary prep

```{r}
# setwd(choose.dir())
d <- read_csv("MKT 382 data 2021 Survey 2.csv")
```
```{r}
typeof(d)
```


```{r}
colnames(d) <- c(
  "timestamp",
  "computer",
  "phone",
  "sports",
  "degree",
  "humor",
  "R",
  "SQL",
  "Python",
  "programming",
  "queso",
  "band",
  "instructor",
  "home",
  "city",
  "math",
  "sleep",
  "late",
  "vegetarian",
  "siblings"
)
```

## Problems and solutions

### Problem 1

Generate a data frame (tibble or equivalent) showing the top three `siblings` values (in descending order). 
The data frame should have only one column: `siblings`. (You can ignore ties.)

```{r}
d %>%
  arrange(-siblings) %>%
  select(siblings) %>%
  slice_head(n=3)
```

### Problem 2

Generate a data frame showing the number of survey responses by degree in descending order of those counts.

```{r}
d %>%
  group_by(degree) %>%
  summarize(count=n()) %>%
  arrange(-count,degree)
```
### Problem 3

Generate a data frame of the mean instructor greatness responses by degree.  The data frame should be in descending order of mean greatness.

```{r}
d %>%
  group_by(degree) %>%
  summarize(mean_greatness=mean(instructor)) %>%
  arrange(-mean_greatness,degree)
```
### Problem 4

For Business majors, the count of responses by computer type.

```{r}
d %>%
  filter(degree=="Business") %>%
  group_by(computer) %>%
  summarize(count=n()) %>%
  arrange(-count,computer)
```
### Problem 5

For Business majors with Macs, the mean number of siblings by queso.  (`mean_siblings` is funny.)

```{r}
d %>%
  filter(degree == "Business", computer == "Mac") %>%
  mutate(mean_siblings=mean(siblings)) %>%
  group_by(queso)%>%
  summarize(mean_siblings=mean(siblings))
```

### Problem 6

Consider a strange metric that is `math+instructor`. This metric, which of course is the
sum of the "how much you like math" response and the "how great is the instructor response",
might have tremendous predictive value. Let's investigate.

Compute the mean value of this metric by `computer` value.

```{r}
d %>%
  mutate(math_instructor = math + instructor) %>%
  group_by(computer) %>%
  summarize(mean(math_instructor))
```

### Problem 7

Generate a `ggplot` histogram of the `math+instructor` values.
```{r}
d%>%
  mutate(math_instructor = math + instructor) %>%
  ggplot(aes(math_instructor))+
  geom_histogram()
```


### Problem 8

For responses reporting one or two siblings, count votes for each `queso`.
```{r}
d %>%
  filter(siblings == "1" | siblings == "2") %>%
  group_by(queso) %>%
  summarize(count=n()) %>%
  arrange(queso,count)
```



